Insert the article title here

### 2018-04-05 writeup/manuscript.tex
minor edit

%%%%%%%%% Insert author address here
\address{$^{1}$Department of Psychology, University of Essex, Colchester, UK\\
$^{2}$Department of Psychology, The Ohio State Universoty, Columbus, USA\\
$^{3}$School of Psychology, University of Aberdeen, Aberdeen, UK
}

@@

\begin{fmtext}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Anybody who has ever run a visual search experiment will be aware of the large differences from one participant to the next, and noting their existence is not new \cite{mackworth1948}. However, these differences are largely ignored and questions about their importance and stability remain relatively under explored.

This seems very relevant \cite{boot2006, boot2009}.

@@

Each search display was composed of 54 small squares (size? What was viewing distance \& screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively. The inner ring was $XX^{\circ}$ and the outer ring was $XX^{\circ}$ from fixation. Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were “variable”. Variable distractors changes colors afrom trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a “red plateau”), then across a period of 7 trials, they would change color from almost red to magenta (at the 4th trial in the transition) to almost blue (see \cite{irons-leber2017}, for the specific color values? Or supplemental?). The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red. This 24-trial cycle would repeat throughout the entire experiment.

@@

Participants were informed that the search displays would contain two targets on every trial, that they need only find one target on each trial and that they were always free to search for either one. A trial began with a 1.5s ITI containing a central fixation cross, followed by the search display until a response was made. Participant responded by pressing a key that corresponded to the digit inside the target (V, B, N and M keys corresponding to 2, 3, 4 and 5 respectively). Participants completed 10 practice trials, followed by 3 blocks of 96 trials. Each block started on a red plateau.

>>>>

%%%%%%%%% Insert author address here
\address{$^{1}$Department of Psychology, University of Essex, Colchester, UK\\
$^{2}$Department of Psychology, The Ohio State University, Columbus, USA\\
$^{3}$School of Psychology, University of Aberdeen, Aberdeen, UK
}

@@

\begin{fmtext}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Anybody who has ever run a visual search experiment will be aware of the large differences from one participant to the next, and noting their existence is not new \cite{mackworth1948}. However, these differences are largely ignored and questions about their importance and stability remain relatively under explored. These differences could be due to several reasons: tiredness\cite{mackworth1948}, speed-accuracy trade-off, motivation, visual impairments, and search strategies\cite{boot2006}.

A striking example of the effect of strategy is given by \cite{boot2006, boot2009}. They found differences in visual search performance could be explained by whether observers used a scanning strategy, or simply fixated the centre of the stimulus and used peripheral vision.

@@

Each search display was composed of 54 small squares (size? What was viewing distance \& screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively. The inner ring was $XX^{\circ}$ and the outer ring was $XX^{\circ}$ from fixation. Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were “variable”. Variable distractors changes colours afrom trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a “red plateau”), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue (see \cite{irons-leber2017}, for the specific colour values? Or supplemental?). The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red. This 24-trial cycle would repeat throughout the entire experiment.

@@

Participants were informed that the search displays would contain two targets on every trial, that they need only find one target on each trial and that they were always free to search for either one. A trial began with a 1.5s ITI containing a central fixation cross, followed by the search display until a response was made. Participant responded by pressing a key that corresponded to the digit inside the target (\texttt{V}, \texttt{B}, \texttt{N} and \texttt{M} keys corresponding to 2, 3, 4 and 5 respectively). Participants completed 10 practice trials, followed by 3 blocks of 96 trials. Each block started on a red plateau.
